Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-22 analysis/paper/paper.Rmd
superscript for plot axis title

density_sp_main_plot <- 
ggplot(kasv_tidy,
       aes(date_age / 1000,
           artefact_density)) +
  geom_point(aes(size = total_artifacts,
                 colour = has_sp)) +
  ylab("Artefact density") +
  xlab("Age of assemblage (ka)") + 
  #geom_smooth(method = "lm") + 
  scale_size_continuous(name = "Total number\nof artifacts")  +
  scale_color_viridis_d(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)  #+
  #geom_text_repel(aes(label = sites),
  #                nudge_x = 0.25, 
  #                nudge_y = 0.25)

>>>>

density_sp_main_plot <- 
ggplot(kasv_tidy,
       aes(date_age / 1000,
           artefact_density)) +
  geom_point(aes(size = total_artifacts,
                 colour = has_sp)) +
  ylab(bquote('Artefact density'~(n/m^3))) +
  xlab("Age of assemblage (ka)") + 
  #geom_smooth(method = "lm") + 
  scale_size_continuous(name = "Total number\nof artifacts")  +
  scale_color_viridis_d(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)  #+
  #geom_text_repel(aes(label = sites),
  #                nudge_x = 0.25, 
  #                nudge_y = 0.25)
